### 2013-09-17 Reports/Report1/reviewedpapers.tex
finishing reviewed papers

\subsection{IRIT \cite{IRIT}}
I found the paper quite interesting as it acquired the first ranking between other participants.

>>>>

\subsection{IRIT \cite{IRIT}}
I found the paper quite interesting as it acquired the first ranking between other participants. Like some other papers, they also create a Vector Space Model and calculate similarity based on cosine measure. The interesting point is that they distinguish between positive and negative preferences and subtract the similarity of negative preferences from positive ones. Therefore the results are most similar to global positive preferences and most dissimilar to global negative preferences.

\subsection{University of Delaware \cite{Delaware}}
The similarity calculation in the paper is very similar to \cite{IRIT}. The main difference is that it uses average of similarity for negative and positive preferences. Time factor is not considered in rating. After rating the final results are filtered based on time.
